Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Clustering and Parameter Estimation

### 2020-09-23 summary.Rmd
updated density plot

ggplot(densities.df) + 
  geom_density(aes(x = inner.prods * sqrt(n), colour = factor(n))) + 
  labs(x = 'between cluster inner products',
       colour = 'n') + 
  scale_colour_brewer(palette = 'Set1')
```

@@

```{r, cache = TRUE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2.'}
A.hh <- readRDS('data/village-hh-59.rds')
zhat.hh <- cluster.pabm(A.hh, 6)
plot.A(A.hh, zhat.hh)
```

>>>>

ggplot(densities.df) + 
  geom_density(aes(x = inner.prods * n, colour = factor(n))) + 
  labs(x = expression(n * v[i]^T * v[j]),
       colour = 'n') + 
  scale_colour_brewer(palette = 'Set1')
```

@@

```{r, cache = TRUE, fig.cap = 'Adjacency matrix of the Karnataka villages data, arranged by the clustering produced by Algorithm 2.', fig.height = 2}
A.hh <- readRDS('data/village-hh-59.rds')
zhat.hh <- cluster.pabm(A.hh, 6)
plot.A(A.hh, zhat.hh)
```
